Adopting agile in the large: motivations, success factors and challenges

### 2014-04-23 journal/article.tex
Reasons to change

As stated by Research Question 1 we investigated the reasons organizations start
a transformation process towards agile software development. In most primary
reasons for starting the transformation were mentioned, and only 7 cases of 42
did not mention any reasons. In the cases giving no specific reason to change it
was simply mentioned that management had decided to change the organization.
The reasons for organizations to change that were found are presented in table
\ref{table:reasonstochange}. The reasons to change were mainly demands for
improvement or identified problems in the current process.

@@

@@

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. A frequent theme was the desire to reduce Time To Market (TTM).

>>>>

As stated by Research Question 1 we investigated the reasons organizations start
a transformation process towards agile software development. In most primary
reasons for starting the transformation were mentioned, and only 7 cases of 42
did not mention any reasons. In the cases giving no specific reason to change it
was simply mentioned that management had decided to change the organization.
The reasons for organizations to change that were found are presented in table
\ref{table:reasonstochange}.

@@

        &  \multicolumn{2}{l}{Something must be done to remain competitive} \\

@@

The reasons to change were are grouped in three top-level categories: external
issues, internal issues, and communication issues. External issues are related
to the business area which the organization is operating in. Internal issues are
related to the way the organization is managed and software is being developed.
Communication issues represent problems in communication and coordination in
software projects.

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. A frequent statement was that it was necessary
to reduce the Time To Market (TTM) [P17, P18, P32, P39, P47]. As stated in one
study ``The market was moving faster than the development group was able to
deliver'' [P38].
